---
title: "Incarceration Analysis"
author: "Jessica Mendoza"
date: "11/21/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction
An introduction of the problem domain and a description of the variable(s) you are choosing to analyze (and why!)
As you introduce your report and the dataset, you should describe the variables that you've chosen to analyze. In doing so, make clear which measure(s) of incarceration you are focusing on. 
how these measure of incarceration vary by race. 


## Summary 
A paragraph of summary information, citing at least 5 values calculated from the data
```{r include=FALSE}
main_df <- read.csv("https://raw.githubusercontent.com/info201b-2021-aut/assignment-3---incarceration-jessica5m/main/incarceration_trends.csv?token=AV5FGDTEUGNMWUEREF7FRQTBUFQAO")

source("https://raw.githubusercontent.com/info201b-2021-aut/assignment-3---incarceration-jessica5m/main/analysis.R?token=AV5FGDVTLHVKBDQGSHIKCATBURMVY")

summary <- list()

#1
summary$avg_ratio <- avg_ratio

#2
summary$highest_jail_pop <- highest_jail_pop

#3 
summary$highest_state_pop <- highest_state_pop

#4
summary$highest_race_pop <- highest_race_pop

#5
summary$highest_race <- highest_race

#6
summary$lowest_race_pop  <- lowest_race_pop

#7
summary$lowest_race <- lowest_race

```

In the [Incarceration Trends](http://trends.vera.org/incarceration-rates?data=pretrial) data set, there are a total of `r (summary$avg_ratio)`, `r (summary$highest_jail_pop)`, `r (summary$highest_state_pop)`,  `r (summary$highest_race_pop)`, `r (summary$highest_race)`, `r (summary$lowest_race_pop)`, `r (summary$lowest_race)`

## Chart 1
In your .Rmd file, make sure to describe why you included the chart, and what patterns emerged

```{r echo=FALSE}
ggplot(division_df, aes(x = year, y = division_df$division_sum, colour = division, group = division)) +
  geom_line() +
  ggtitle("Change In Jail Population By Division, From 1970-2018") +
  xlab("Year") +
  ylab("Jail Population")
```

#### Summary

## Chart 2
In your .Rmd file, make sure to describe why you included the chart, and what patterns emerged

```{r echo=FALSE}
ggplot(ratio_race_df, aes(x=total_jail_pop, y=value, colour= variable)) + 
  geom_point() +
  scale_colour_manual("Ethnicity", values = c("purple", "orange", "red", "dark green", "navyblue", "pink"), labels = c("Asian American/Pacific Islander", "Latinx American", "African American", "Native American", "Caucasian", "Other")) +
  ggtitle("Total Incarceration Population vs. Ethnic Population") +
  xlab("Total Incarceration Population") +
  ylab("Ethnic Population/Total Incarceration Population Ratio")
```

#### Summary

## Map

Your map needs a title
Your color scale needs a legend with a clear label
Use a map based coordinate system to set the aspect ratio of your map (see reading)
Use a minimalist theme for the map (see reading)
In your .Rmd file, make sure to describe why you included the chart, and what patterns emerged

```{r echo=FALSE}
ggplot() +
  geom_polygon( data= map_df, aes(long,lat, group = group, fill = percent_incarcerated), color="white", size = 0.5) +
  ggtitle("Percentage Of Population That Is Incarcerated") +
  scale_fill_continuous(name="Percentage",low = "lightblue", high = "navyblue") +
  blank_theme
```

#### Summary 

